Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
visualizing dispersal of seeds

Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
```{r message=FALSE}
nruns <- 10

@@

df %>% 
  ggplot(., aes(x = xloc, y=yloc, 
                #group = run,
                color = indiv)) +
  facet_wrap(~run) +
  geom_path() +
  scale_color_manual(values = mycols) +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
  theme_bw()

summ.df %>% 
  ggplot(., aes(y = dsprsn)) +
  geom_boxplot()
```

>>>>

Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
```{r message=FALSE}
nruns <- 100

@@

df %>% 
  ggplot(., aes(x = xloc, y=yloc, 
                group = run,
                color = indiv)) +
  # facet_wrap(~run) +
  geom_path() +
  scale_color_manual(values = mycols) +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
  theme_bw()

summ.df %>% 
  ggplot(., aes(y = dsprsn)) +
  geom_boxplot()

summ.df %>% 
  ggplot(., aes(x = av.disp)) +
  geom_density(color = "blue") + # for the average dispersal per run
  geom_density(data = df %>% drop_na(s.id),
                 aes(x = disp)) + # for every seed
  theme_bw()
```
